---
title: "01_Wojcik_Abigail_2022"
author: "AW"
format: html
editor: visual
---

## Homework 1

## Question 1

```{r first_chunk}
data(quakes)
head(quakes)
str(quakes)
summary(quakes)

```

I see that there are 1000 observations entered into the data set "quakes" and 5 variables: lat, long, depth, mag, and stations. I can also see the minimums/maximums, first/third quartiles, means/medians for all of the variables.

## Question 2/3

```{r second_chunk}
quakes[,"long"] #pull up column "long" in dataset "quakes"
unq_vector <-c(5:8, 1,3,3,9, 12:4)
unique(unq_vector)
length(unique(quakes$stations)) #one way to do it, integer
length(unique(quakes[["stations"]])) #another way to do it, integer
cat("There are", length(unique(quakes$stations)), "unique stations." )


```

There are 102 unique stations.

## Question 4/ "Impress Yourself"

```{r third_chunk}
range(quakes$depth) #what is the range of depths of earthquake occurrence 
max(quakes$mag) # largest earthquake
which(quakes == max(quakes$mag), arr.ind = TRUE) # the largest quake is at location row = 152, column = 4
lat <- quakes$lat[152]
long <- quakes$long[152]
lat
long
cat("largest earthquake location =", lat, "latitude,", long, "longitude with magnitude", max(quakes$mag))
```

The range of depths in which earthquakes occur is 40 - 680.

The largest earthquake magnitude was 6.4 at latitude -15.56 and longitude 167.62.

Meta 1:

This was a little hard, but I enjoyed it.

Meta 2:

This took me about 2 hours, most of which was the "impress yourself" question

Meta 3:

I would say I did a sufficient job? I guess I'll find out, won't I. I just don't feel very confident about any of my work.
